From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-09 Pi+/paper/equivalence.tex
Fixes
Fix appendix ref

We present the types and 1-combinators of $\PiPlusLang$ and $\PiHatLang$ in~\Cref*{fig:piplus,fig:pihat} respectively,
eliding the 2-combinators for brevity. We enforce that there is a unique 2-combinator between compatible 1-combinators,
by relating them with a truncation. These can be found in the appendix and in the accompanying Agda code
(~\cref{app:level-two}).

@@

\begin{definition}
  \begin{gather*}
    \begin{aligned}
      \gdenot{\blank}_{0} &\defeq \evalh_{0} \comp \evalp_{0} \comp \evalt_{0}
    \end{aligned}
    \qquad
    \begin{aligned}
      \gdenot{\blank}_{1} &\defeq \evalh_{1} \comp \evalp_{1} \comp \evalt_{1}
    \end{aligned}
  \end{gather*}
\end{definition}

\begin{theorem}[Full Abstraction and Adequacy]
  If $c_1, c_2 : X \iso Y$, then $\denot{c_1} = \denot{c_2}$ iff $\gdenot{c_1}_{1} = \gdenot{c_2}_{1}$.
\end{theorem}

>>>>

We present the types and 1-combinators of $\PiPlusLang$ and $\PiHatLang$ in~\Cref*{fig:piplus,fig:pihat} respectively,
eliding the 2-combinators for brevity. We enforce that there is a unique 2-combinator between compatible 1-combinators,
by relating them with a truncation. These can be found in the appendix and in the accompanying Agda code
(~\cref{app:leveltwo}).

@@

\begin{definition}[${\gdenot{\blank}}$]
  \begin{gather*}
    \begin{aligned}
      \gdenot{\blank}_{0} &: U \to \UFin \\
      \gdenot{\blank}_{0} &\defeq \evalh_{0} \comp \evalp_{0} \comp \evalt_{0}
    \end{aligned}
    \qquad
    \begin{aligned}
      \gdenot{\blank}_{0} &: X \iso Y \to \gdenot{X}_{0} \id_{\UFin} \gdenot{Y}_{0} \\
      \gdenot{\blank}_{1} &\defeq \evalh_{1} \comp \evalp_{1} \comp \evalt_{1}
    \end{aligned}
  \end{gather*}
\end{definition}

\begin{theorem}[Full Abstraction and Adequacy]
  For any $c_1, c_2 : X \iso Y$, we have that
  \[
    \denot{c_1} = \denot{c_2} \text{ if and only if } \gdenot{c_1}_{1} = \gdenot{c_2}_{1}
  \]
\end{theorem}
